An efficient acyclic contact planner for multiped robots

### 2017-01-13 body/conclusion.tex
[Discussion]

 \section{Discussion} 
\label{sec:discussion}

\subsection{validity and interest of the approximations}

TODO equilibirum as contact reachability

@@

Figure~\ref{fig:dedefeas} gives an insight into the difference between the three conditions, depicting $C_{Equil}^0$, $C_{Contact}^0$ and $C_{Reach}^0$, which are the sets of \gls{equilibrium feasible}, \gls{contact reachable} and \textit{reachable} root configurations, respectively.

TODO blah regarding contact plan generation, and ignoring the mid contact conf
The first constraint is less restrictive than the one proposed by \citeauthor{DBLP:conf/iser/EscandeKMG08}, because our method
allows to break and create one contact

>>>>

 \section{Discussion: validity and interest of our contact planner} 
\label{sec:discussion}

\subsection{Accuracy and performance gain of the reachability condition}

As demonstrated in the results section, the main interest of our method is time performance. Time performance is critical to consider using a multi-contact planner for 
online applications with the robot, a goal not satisfied by any of the previous contributions. Our method addresses highly constrained environments while improving the search time by orders of magnitude. This high performance is reached at the cost of some approximations we discuss here. 
%~ In previous approaches, we identified 2 sources of high computational cost.

The first approximation is the verification of \contactreachability\ ($\mathbf{q}^0 \in C_{Contact}^0$).  Our \textit{reachability condition} ($\mathbf{q}^0 \in C_{Reach}^0$) is computationally efficient and provides an accurate approximation of $C_{Contact}^0$ (Section~\ref{sec:scaling}). This is demonstrated by the second column of Table~\ref{tab:requestpercent}, and illustrated by Figure~\ref{fig:dedefeas}. Indeed, in the large majority of cases, (84\% in the worst case), we are able to find a contact configuration for any configuration in $C_{Reach}^0$.

%~ These results clearly demonstrate that the reachability condition, presented in Section~\ref{sec:scaling}, provides an accurate representation of the 
%~ contact we combine only-necessary and only-sufficient conditions which are trivial to estimate. Only-necessary conditions are appealing because they preserve the completeness of the search, while reducing 
%~ the search space: they provide an outer approximation of $C_{Contact}^0$. On the other hand, only-sufficient conditions provide the guarantee that any configuration that satisfies them is indeed \gls{contact reachable}: they provide an inner approximation of $C_{Contact}^0$.

The main source of computational cost identified in previous works is the verification of \equilibriumfeasibility. 
The strong assumption of our work is that for the class of problems we consider \contactreachability\ implies \equilibriumfeasibility.
Our scenarios show that the  assumption is verified in the majority of cases when at least one contact surface is \textit{quasi flat}, that is when
the friction cone of the contact surface contains the direction opposite to the gravity.
Figure~\ref{fig:dedefeas} illustrate this observation, demonstrated empirically by the third column of Table~\ref{tab:requestpercent}. In the worst case, in our experiment
the assumption was verified for 82\% of the total amount of trials.

In the example of \cite{Bouyarmane2009}, the verification of \equilibriumfeasibility implies a constructive demonstration by exhibiting a valid $\mathbf{q}^{\overline{0}}$, requiring
several minutes of planning. Our method, in comparison, takes from a few milliseconds to several seconds.

These results clearly justify the pragmatic decisions of this paper. What is lost in completeness is largely compensated by the computation times we obtain.

\subsection{Addressing $\mathcal{P}_3$}
This paper focuses on the contact planning aspect of multi-contact locomotion. While it does not address directly the continuous motion generation,
we had to prove that the plans produced by our planner are useful and can be executed by the considered robots. The problem $\mathcal{P}_3$ remains open,
and most existing solutions do not consider collisions with the environment during the planning, making it hard to validate constrained problems such as the polaris scenario
or the table egress in \cite{DBLP:conf/iser/EscandeKMG08}.
The companion video shows the results we obtained in simulation and on the real HRP-2 robot. Despite the fact that our method does not consider joint torque limits in the planning
phase, the robot is able to execute our plans, achieving to demonstrate the interest of our framework.

@@

### 2017-01-13 body/results.tex
[Discussion]

\subsubsection{Success rates:}
Table~\ref{tab:sucess_planning} summarizes the successful planning rates obtained for each scenario.
Despite the complexity of the scenarios adressed, as well as the approximations made in our formulation, our planner succeeds in a large majority of cases.

@@

These results confirm that our approach provides a satisfying compromise between completeness and efficiency, thus allowing to consider online planning
while controlling the robot.
Indeed, when the contact generation fails, it does so rapidly, which allows us to rapidly re-plan with a reasonable chance of success.
The most efficient (and immediate) approach to obtain a valid contact plan as fast as possible is probably to launch in parallel several instances of the planner (our current implementation is single-threaded) and to use any successful result as a plan for solver $\mathcal{P}_3$.

>>>>

\subsubsection{Success rates:}
Table~\ref{tab:sucess_planning} summarizes the successful planning rates obtained for each scenario.
Despite the complexity of the scenarios adressed, as well as the approximations made in our formulation, our planner succeeds in the large majority of cases.

@@

These results confirm that our approach provides a satisfying compromise between completeness and efficiency, thus allowing to consider online planning
while controlling the robot. Indeed, when the contact planning fails, it does so rapidly, which allows us to rapidly re-plan with a reasonable chance of success.
The most efficient (and immediate) approach to obtain a valid contact plan as fast as possible is probably to launch in parallel several instances of the planner (our current implementation is single-threaded) and to use any successful result as a plan for solver $\mathcal{P}_3$.
